---
title: "3a-Question1-R-legume"
output: html_document
date: "2023-03-17"
Authors: Kathryn Bloodworth, Smriti Pehim Limbu, Kimberly Komatsu
---

```{r load working directory & packages, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# load packages
pacman::p_load(ggplot2, lme4,lmerTest, tidyverse, dplyr, readr)
# set working directory for Kathryn - mac
knitr::opts_knit$set(root.dir = '/Volumes/GoogleDrive/My Drive/Projects/Legume-Meta Analysis/Data')
```

```{r Set ggplot base}
#Set ggplot2 theme to black and white
theme_set(theme_bw())
#Update ggplot2 theme - make box around the x-axis title size 30, vertically justify x-axis title to 0.35, Place a margin of 15 around the x-axis title.  Make the x-axis title size 30. For y-axis title, make the box size 30, put the writing at a 90 degree angle, and vertically justify the title to 0.5.  Add a margin of 15 and make the y-axis text size 25. Make the plot title size 30 and vertically justify it to 2.  Do not add any grid lines.  Do not add a legend title, and make the legend size 20
theme_update(axis.title.x=element_text(size=30, vjust=-0.35, margin=margin(t=15)),
             axis.text.x=element_text(size=30), axis.title.y=element_text(size=30, angle=90, vjust=0.5,
                                                                          margin=margin(r=15)), axis.text.y=element_text(size=30), plot.title =
               element_text(size=30, vjust=2), panel.grid.major=element_blank(),
             panel.grid.minor=element_blank(), legend.title=element_blank(),
             legend.text=element_text(size=40))
```

### Starting a new analysis and this chunk is for loading files, Plant_Associations is the cleaned file
```{r Load in Plant Associations and clean}
Clean_Species<-read_csv("legume_clean_names.csv") %>% 
  filter(old_genus_species!="") %>% 
  separate(old_genus_species,c("genus","species","subspecies","extra"),sep=" ") %>% 
  unite(col=genus_species, c(genus,species,subspecies,extra), sep='_',na.rm=TRUE)


Plant_Associations<-read.csv("legume_strain diversity_meta analysis_plant associations_edited names_presence absence.csv") %>% pivot_longer(names_to = "rhizobia_sp", values_to = "presence_absence", cols=Bradyrhizobium_nitroreducens:Paraburkholderia_caribensis)

##Now filtering out row crop and 999, 0 and 1 presence and absence and joining clean_species
Plant_Associations_Clean <- Plant_Associations %>%
  left_join(Clean_Species) %>%
  filter(cultivation.status!="row crop", genus_species!="999", presence_absence=="1", plant_status!="999", species!="sp",species!="spp",species!="sp.",paper_id!=142, plant_status!="extinct") %>% 
filter(!(sample_country %in% c("Japan-China","Japan_China","Kenya-Sudan","Czech_Republic-France-Georgia-Hungary-Italy-Romania-Spain","Senegal-Mauritania-Tunisia-Burundi","Malawi-Zambia-Kenya","Brazil-Venezuela"))) %>% 
  select(-introduced,-invasive,-cultivated) %>% 
  rename(paper_plant_status=plant_status) %>% 
  mutate(global_plant_status=ifelse((exo_NA+exo_SA+exo_AU+exo_AS+exo_EU+exo_AF)>0,1,0)) %>% 
  filter(num_nodules>4)

colnames(Plant_Associations_Clean)

```

```{r Load in Plant Associations and clean}
Plant_Data<-read.csv("legume_strain diversity_meta analysis_plant data.csv")

##Now filtering out row crop and 999, 0 and 1 presence and absence and joining clean_species
Plant_Data_Clean <- Plant_Data %>%
  rename(notes_plantdata=notes) %>% 
  left_join(Clean_Species) %>%
  filter(cultivation.status!="row crop", genus_species!="999", species!="sp",species!="spp",species!="sp.",paper_id!=142) %>% 
  filter(num_nodules>4)

colnames(Plant_Data_Clean)

```

```{r Create dataframe with just papers where native/non natives were studied within a given location }

#Create a new dataframe that has only plant associations with species 
Plant_Status<-Plant_Associations_Clean %>% 
  select(paper_id,genus_species,new_name,cultivation.status,global_plant_status,paper_plant_status) %>% 
  mutate(global_plant_status=ifelse(global_plant_status==1,"nonnative","native")) %>% 
  mutate(paper_plant_status=ifelse(paper_plant_status=="invasive","nonnative",ifelse(paper_plant_status=="introduced","nonnative", paper_plant_status))) %>% 
  unique()

Native_NonNative_Fig1 <- Plant_Data_Clean %>%
  #merge plant associations so that we can determine plant status, etc.
  merge(Plant_Status,by = c("paper_id", "genus_species", "new_name", "cultivation.status"),all=TRUE) %>% 
  select(paper_id,genus_species, new_name,paper_plant_status,annual_perennial,growth_form,sample_country,sample_continent,sites_sampled,num_nodules,num_plants,strain_richness,proportion_overlapping_strains,num_spp_compared,compares_natinv) %>% 
   #only keep papers that looked at native and non native species within the same location
  filter(compares_natinv==1) %>% 
  na.omit(plant_paper_status)

Native_NonNative_Fig1$strain_richness=as.numeric(Native_NonNative_Fig1$strain_richness)

```


```{r Create Figure for Question 1: Boxplot}

ggplot(Native_NonNative_Fig1,aes(x=paper_plant_status,y=as.numeric(strain_richness))) +
  geom_boxplot()+
  scale_x_discrete(labels = c("Native", "Non Native"), breaks = c("native","nonnative"))+
  xlab("Plant Status")+
  ylab("Rhizobial Strain Richness")+
  expand_limits(y=c(0,30))
  
```

```{r Create Figure for Question 1: Violin Plot }

ggplot(Native_NonNative_Fig1,aes(x=paper_plant_status,y=as.numeric(strain_richness))) +
  geom_violin()+
  scale_x_discrete(labels = c("Native", "Non Native"), breaks = c("native","nonnative"))+
  xlab("Plant Status")+
  ylab("Rhizobial Strain Richness")+
  expand_limits(y=c(0,30))
  
```

```{r LMER native/non natives within a given location}
Native_NonNative_Fig1

Native_NonNative_lmer <- lmerTest::lmer(data = Native_NonNative_Fig1, strain_richness ~ paper_plant_status*growth_form + (1|paper_id) + (1|new_name))
anova(Native_NonNative_lmer) #NS

Native_NonNative_lmer <- lmerTest::lmer(data = Native_NonNative_Fig1, strain_richness ~ paper_plant_status*growth_form + (1|paper_id) + (1|new_name) + (1|num_nodules))
anova(Native_NonNative_lmer) #NS
  
```























##Strains in native versus non-natives, grouping by species and plant status and rhizobial_sp, and total number of nodules per species and plant status

```{r}
#convert 999 in num_nodules to NA
Plant_Associations_num <- Plant_Associations_Clean %>%
  mutate(num_nodules=ifelse(num_nodules=="999", NA, num_nodules)) %>% 
  mutate(num_plants=ifelse(num_plants=="999", NA, num_plants))

# create new column where we add up the total number of nodules across plant species, plant status (within paper) and rhizobia species so that we can use total_nodules in future statistical models
native_nonnative.strains <- Plant_Associations_num %>%
  group_by(genus_species,paper_plant_status,rhizobia_sp) %>%
  summarise(total_nodules=sum(num_nodules)) %>%
  ungroup()

```

## Loading strain diversity and sequence information

```{r}

#Read in strain diversity info and add NA for anywhere that has a blank
Strain_Diversity<-read.csv("legume_strain diversity_meta analysis_strain sequences.csv") 
Strain_Diversity[Strain_Diversity==""]<-NA

#Read in strain sequence information
accession_numbers<-read.csv("legume_strain diversity_meta analysis_strain sequences.csv",stringsAsFactors = FALSE,na.strings="") 

```
##Basic info about study

```{r}
## Determine number of papers assessed (327) , We are also removing paper 140 which was about moss, now we have 326
Manuscript_Info<-read.csv("legume_strain diversity_meta analysis_paper information.csv")
Manuscript_Info[Manuscript_Info==""]<-NA

#Removing papers that had comments saying it was a review or irrelevant or didnt exist
#calculation the number of papers for the study
Manuscript_Info %>% filter(paper_id!=313 & paper_id!=312 & paper_id!=317& paper_id!=140) %>% 
  group_by(paper_id, author, year)%>%
  unique()%>%
  summarise(num_papers=length(paper_id))%>%
  ungroup() %>% 
  summarise(papers=length(paper_id))%>%
  summarise(num_papers=sum(papers))

## Determine number plant species (555)
Plant_Associations_Clean %>%
  group_by(new_name)%>%
  unique()%>%
  summarise(num_species=length(new_name))%>%
  ungroup()%>%
  summarise(num_species=length(new_name))

## Determine number of countries 85 -- this is not an accurate number (and we don't think it matters)
# Plant_Associations%>%
#   group_by(sample_country)%>%
#   unique()%>%
#   summarise(num_countries=length(sample_country))%>%
#   ungroup()%>% 
#   summarise(num_countries=length(sample_country))
```
#### Basic Data Analyses ####

#### Introduced vs. Native ####
```{r}

# Create data frame with native vs. introduced species
Introduced_native_Number<- Plant_Associations_Clean%>%
  mutate(paper_plant_status=ifelse(paper_plant_status %in% c("introduced","invasive","introduced-native"),"non-native",ifelse(paper_plant_status==" native","native",paper_plant_status))) %>%
  group_by(paper_plant_status)%>%
  unique()%>%
  summarise(plant_status_counts=length(paper_plant_status))%>%
  ungroup()

#Make graph showing number of species and plant species status
ggplot(Introduced_native_Number,aes(x=paper_plant_status,y=plant_status_counts,fill=paper_plant_status))+
  #Make a bar graph where the height of the bars is equal to the data (stat=identity) and you preserve the vertical position while adjusting the horizontal(position_dodge), and outline the bars with the color black.
  geom_bar(stat="identity", position=position_dodge(),color="black")+
  #make error bars using the Standard error from the mean and place them at 0.9 with a width of 0.2
  #Label the x-axis "Watershed"
  xlab("Plant Species Status")+
  #Label the y-axis "Species Richness"
  ylab("Number of Observations")+
  expand_limits(y=1000)+
  #Fill the bar graphs with grey and white according and label them "Inside Fence" and "Outside Fence"
  scale_fill_manual(values=c("darkslategrey","cadetblue4"), labels=c("Native", "Non-Native"))  

```

#### Rhizobial Associates by plant status ####

```{r}

#Make a new data frame called Wide_rhizobial_associations 
Rhizobial_Associations<-Plant_Associations%>%
  mutate(Plant_status=ifelse(plant_status=="introduced","non_native",ifelse(plant_status=="invasive","non_native",ifelse(plant_status=="native","native",ifelse(plant_status=="extinct","extinct",ifelse(plant_status=="introduced-native","non_native",ifelse(plant_status==" native","native",plant_status)))))))
colnames(Rhizobial_Associations)

#Sum across all columns with presence absence data for each row, giving us the number of associations for each species from each paper (change made here)
Rhizobial_Associations<- Rhizobial_Associations %>% 
  group_by(genus_species) %>% 
 mutate(diversity_sum = length(unique(rhizobia_sp)))


#Make a new condensed dataframe with only necessary information
Rhizobial_Associations_Condensed<-Rhizobial_Associations %>% 
  select(paper_id, genus_species, sample_country,diversity_sum,Plant_status, num_nodules) %>% 
  filter(Plant_status!="extinct") %>% 
  na.omit()

#Make a data frame calculating the mean, standard error, and number of observations for native vs. non-native to make graph
Average_rhizobial_symbionts_genus_sp<-Rhizobial_Associations_Condensed%>%
  group_by(Plant_status,genus_species)%>%
  summarize(symbionts_Std=sd(diversity_sum),symbionts_Mean=mean(diversity_sum),species_status_n=length(diversity_sum))%>%
  #Make a new column called "Richness_St_Error" and divide "Richness_Std" by the square root of "Richness_n"
  mutate(symbionts_St_Error=symbionts_Std/sqrt(species_status_n)) %>% 
  ungroup()

#Make a data frame calculating the mean, standard error, and number of observations for native vs. non-native to make graph
Average_rhizobial_symbionts_Graph<-Average_rhizobial_symbionts_genus_sp%>%
  group_by(Plant_status)%>%
  summarize(symbionts_Std=sd(symbionts_Mean),symbionts_Mean2=mean(symbionts_Mean),status_n=length(symbionts_Mean))%>%
  #Make a new column called "Richness_St_Error" and divide "Richness_Std" by the square root of "Richness_n"
  mutate(symbionts_St_Error=symbionts_Std/sqrt(status_n)) %>% 
  ungroup() %>% filter(Plant_status!="999")


#Make graph showing number of introduced vs. native
ggplot(Average_rhizobial_symbionts_Graph,aes(x=Plant_status,y=symbionts_Mean2,fill=Plant_status))+
  #Make a bar graph where the height of the bars is equal to the data (stat=identity) and you preserve the vertical position while adjusting the horizontal(position_dodge), and outline the bars with the color black.
  geom_bar(stat="identity", position=position_dodge(),color="black")+
  geom_errorbar(aes(ymin=symbionts_Mean2-symbionts_St_Error,ymax=symbionts_Mean2+symbionts_St_Error),position=position_dodge(0.9),width=0.2)+
  #make error bars using the Standard error from the mean and place them at 0.9 with a width of 0.2
  #Label the x-axis "Watershed"
  xlab("Plant Species Status")+
  #Label the y-axis "Species Richness"
  ylab("Average Number of Symbionts")+
  #Fill the bar graphs with grey and white according and label them "Inside Fence" and "Outside Fence"
  scale_fill_manual(values=c("darkslategrey","cadetblue4"), labels=c("Native","Non-native"))  

#histogram for Rhizobial Associations
hist(Rhizobial_Associations_Condensed$diversity_sum)

#### K question -- which one? ####

#Run anova comparing # of symbionts by plant status accounting for how many studies per species 
summary (Mixed_Model_Rhiz_Status<- lmer(symbionts_Mean ~ Plant_status + (1 | species_status_n), data = Average_rhizobial_symbionts_genus_sp))
#anova accounting for type II error - for unbalanced data or interaction terms that are significant 
anova(Mixed_Model_Rhiz_Status,type = 2)

#random effect -- i think this is correct
summary(Mixed_Model_Rhiz_Status_NoMean_Random<- lmer(diversity_sum ~ Plant_status + (1 | genus_species) + (1 | num_nodules), data = Rhizobial_Associations_Condensed)) 
#anova accounting for type II error - for unbalanced data or interaction terms that are significant 
anova(Mixed_Model_Rhiz_Status_NoMean_Random,type = 2) 
```


#### Rhizobial Associates by Growth Form  ####

```{r}
Plant_Data<-read.csv("legume_strain diversity_meta analysis_plant data.csv") %>% 
  left_join(Clean_Species) %>% 
  select(genus_species,new_name,1:32)
Plant_Data[Plant_Data==""]<-NA

Plant_Data_simplified<-Plant_Data %>% 
  select(paper_id,author,year,genus_species,annual_perennial,growth_form)

#Make a new data frame called rhizobial_associates_growth_form
Rhizobial_Associations_growth_form<-Plant_Associations%>%
  mutate(Plant_status=ifelse(plant_status=="introduced","non_native",ifelse(plant_status=="invasive","non_native",ifelse(plant_status=="native","native",ifelse(plant_status=="extinct","extinct",ifelse(plant_status=="introduced-native","non_native",ifelse(plant_status==" native","native",plant_status))))))) %>% 
  left_join(Plant_Data_simplified)

#Sum across all columns with presence absence data for each row, giving us the number of assiciations for each species from each paper
Rhizobial_Associations_growth_form <- Rhizobial_Associations_growth_form %>% 
  group_by(genus_species) %>% 
 mutate(diversity_sum = length(unique(rhizobia_sp)))

#Make a new condensed dataframe with only necessary information
Rhizobial_Associations_GF_Condensed<-Rhizobial_Associations_growth_form %>% 
  select(paper_id, genus_species, sample_country,diversity_sum,annual_perennial,growth_form,num_nodules,Plant_status) %>% 
  na.omit() %>% 
  filter(Plant_status %in% c("native","non_native"))

#Make a data frame calculating the mean, standard error, and number of observations for native vs. non-native to make graph
Average_growth_form_Graph<-Rhizobial_Associations_GF_Condensed%>%
  group_by(growth_form)%>%
  summarize(symbionts_Std=sd(diversity_sum),symbionts_Mean=mean(diversity_sum),symbionts_n=length(diversity_sum))%>%
  #Make a new column called "Richness_St_Error" and divide "Richness_Std" by the square root of "Richness_n"
  mutate(symbionts_St_Error=symbionts_Std/sqrt(symbionts_n))

#Make graph showing number of introduced vs. native
ggplot(Average_growth_form_Graph,aes(x=growth_form,y=symbionts_Mean,fill=growth_form))+
  #Make a bar graph where the height of the bars is equal to the data (stat=identity) and you preserve the vertical position while adjusting the horizontal(position_dodge), and outline the bars with the color black.
  geom_bar(stat="identity", position=position_dodge(),color="black")+
  geom_errorbar(aes(ymin=symbionts_Mean-symbionts_St_Error,ymax=symbionts_Mean+symbionts_St_Error),position=position_dodge(0.9),width=0.2)+
  #make error bars using the Standard error from the mean and place them at 0.9 with a width of 0.2
  #Label the x-axis "Watershed"
  xlab("Growth Form")+
  #Label the y-axis "Species Richness"
  ylab("Average Number of Symbionts")#+
  #scale_fill_manual(values=c("darkslategrey","cadetblue4","cadetblue3"))  


####Anova for growth form ####
summary(Mixed_Model_Rhiz_Status_Growth_Form<- lmer(diversity_sum ~ growth_form + (1|num_nodules), data = Rhizobial_Associations_GF_Condensed)) #
anova(Mixed_Model_Rhiz_Status_Growth_Form,type=2)

```

#### Rhizobial Associates by Annual/Perennial  ####

```{r}
#Make a data frame calculating the mean, standard error, and number of observations for native vs. non-native to make graph
Average_annual_perennial_Graph<-Rhizobial_Associations_GF_Condensed%>%
  group_by(annual_perennial,Plant_status)%>%
  summarize(symbionts_Std=sd(diversity_sum),symbionts_Mean=mean(diversity_sum),symbionts_n=length(diversity_sum))%>%
  #Make a new column called "Richness_St_Error" and divide "Richness_Std" by the square root of "Richness_n"
  mutate(symbionts_St_Error=symbionts_Std/sqrt(symbionts_n))

#Make graph showing number of introduced vs. native and perennial / annual
ggplot(Average_annual_perennial_Graph,aes(x=annual_perennial,y=symbionts_Mean,fill=Plant_status))+
  #Make a bar graph where the height of the bars is equal to the data (stat=identity) and you preserve the vertical position while adjusting the horizontal(position_dodge), and outline the bars with the color black.
  geom_bar(stat="identity", position=position_dodge(),color="black")+
  geom_errorbar(aes(ymin=symbionts_Mean-symbionts_St_Error,ymax=symbionts_Mean+symbionts_St_Error),position=position_dodge(0.9),width=0.2)+
  #make error bars using the Standard error from the mean and place them at 0.9 with a width of 0.2
  #Label the x-axis "Watershed"
  xlab("Growth Timing")+
  #Label the y-axis "Species Richness"
  ylab("Average Number of Symbionts")
#scale_fill_manual(values=c("darkslategrey","cadetblue4"))  

#Make a data frame calculating the mean, standard error, and number of observations for native vs. non-native to make graph
Average_status_herb_Graph<-Rhizobial_Associations_GF_Condensed %>%
  mutate(Growth_Status=paste(growth_form,annual_perennial,sep = "::")) %>% 
  group_by(Growth_Status,Plant_status) %>%
  summarize(symbionts_Std=sd(diversity_sum),symbionts_Mean=mean(diversity_sum),symbionts_n=length(diversity_sum)) %>%
  #Make a new column called "Richness_St_Error" and divide "Richness_Std" by the square root of "Richness_n"
  mutate(symbionts_St_Error=symbionts_Std/sqrt(symbionts_n))

#Make graph showing number of introduced vs. native and herb/woody and annual/perennial
ggplot(subset(Average_status_herb_Graph,Growth_Status!="woody::annual"),aes(x=Growth_Status,y=symbionts_Mean,fill=Plant_status))+
  #Make a bar graph where the height of the bars is equal to the data (stat=identity) and you preserve the vertical position while adjusting the horizontal(position_dodge), and outline the bars with the color black.
  geom_bar(stat="identity", position=position_dodge(),color="black")+
  geom_errorbar(aes(ymin=symbionts_Mean-symbionts_St_Error,ymax=symbionts_Mean+symbionts_St_Error),position=position_dodge(0.9),width=0.2)+
  #make error bars using the Standard error from the mean and place them at 0.9 with a width of 0.2
  #Label the x-axis "Watershed"
  xlab("Growth Timing")+
  #Label the y-axis "Species Richness"
  ylab("Average Number of Symbionts")#+
#scale_fill_manual(values=c("darkslategrey","cadetblue4"))  

####Anova for annual/perennial ####
summary(Mixed_Model_Rhiz_Status_A_P<- lmer(diversity_sum ~ annual_perennial + (1|num_nodules), data = Rhizobial_Associations_GF_Condensed)) #
anova(Mixed_Model_Rhiz_Status_A_P,type=2) 

#t.test(Rhizobial_Associations_GF_Condensed$diversity_sum~Rhizobial_Associations_GF_Condensed$annual_perennial) 

####Anova for annual/perennial*native/nonnative ####
summary(Mixed_Model_Rhiz_Status_A_P_Plant_status<- lmer(diversity_sum ~ annual_perennial*Plant_status + (1 | genus_species) + (1|num_nodules), data = Rhizobial_Associations_GF_Condensed))
#type 3 is used because we have an interaction
anova(Mixed_Model_Rhiz_Status_A_P_Plant_status,type = 3) 

####Anova for annual/perennial*native/nonnative*growth form ####
summary(Mixed_Model_Rhiz_Status_A_P_Status_GF<- lmer(diversity_sum ~ annual_perennial*Plant_status + growth_form*Plant_status + (1 | genus_species) + (1|num_nodules), data = Rhizobial_Associations_GF_Condensed)) #
anova(Mixed_Model_Rhiz_Status_A_P_Status_GF,type = 3) 

```

#### Number Nodules (sample number) by strain richness ####

```{r}

Nod_by_strain<-Plant_Data %>%
  filter(strain_richness!="NEED SUPPLEMENTAL PAPER")%>%
  filter(!is.na(num_nodules),!is.na(strain_richness))%>% 
  mutate(strain_richness=as.numeric(strain_richness)) %>% 
  filter(num_nodules>10) %>% 
  group_by(genus_species) %>% 
  summarize(num_nod_Mean=mean(num_nodules),num_nod_n=length(num_nodules),strain_rich_Mean=mean(strain_richness),strain_rich_n=length(strain_richness))%>%
  ungroup()

hist(Nod_by_strain$num_nod_Mean) 

#graph looking at strain richness by nodule number
ggplot(Nod_by_strain,aes(y=strain_rich_Mean,x=num_nod_Mean))+
  geom_point()+
  geom_smooth()+
  #keep entire graph but zoom in on certain area
  coord_cartesian(xlim=c(0,100))

#merge plant status with number of nodules
Rhiz_symbionts_Nod_Num<-Nod_by_strain %>% 
  left_join(Average_rhizobial_symbionts_genus_sp) %>% 
  select(-symbionts_Std,-symbionts_St_Error) %>% 
  filter(!is.na(num_nod_Mean),!is.na(Plant_status))

#look at difference between strain richness number and symbionts number
ggplot(Rhiz_symbionts_Nod_Num,aes(y=strain_rich_Mean,x=symbionts_Mean))+
  geom_point()+
  geom_abline()

#make dataframe for graph
Strain_rich_graph<-Rhiz_symbionts_Nod_Num %>% 
  group_by(Plant_status) %>% 
  summarize(strain_rich_Mean2=mean(strain_rich_Mean),strain_rich_n2=length(strain_rich_Mean),strain_rich_Std=sd(strain_rich_Mean))%>%
  mutate(strain_rich_St_Error=strain_rich_Std/sqrt(strain_rich_n2)) %>% 
  ungroup()

#Make graph showing average strain richness by introduced vs. native
ggplot(Strain_rich_graph,aes(x=Plant_status,y=strain_rich_Mean2,fill=Plant_status))+
  #Make a bar graph where the height of the bars is equal to the data (stat=identity) and you preserve the vertical position while adjusting the horizontal(position_dodge), and outline the bars with the color black.
  geom_bar(stat="identity", position=position_dodge(),color="black")+
  geom_errorbar(aes(ymin=strain_rich_Mean2-strain_rich_St_Error,ymax=strain_rich_Mean2+strain_rich_St_Error),position=position_dodge(0.9),width=0.2)+
  #make error bars using the Standard error from the mean and place them at 0.9 with a width of 0.2
  #Label the x-axis "Watershed"
  xlab("Plant Species Status")+
  #Label the y-axis "Species Richness"
  ylab("Average Strain Richness")#+
  #scale_fill_manual(values=c("darkslategrey","cadetblue4"), labels=c("Native","Non-native"))  

hist(Rhizobial_Associations_Condensed$diversity_sum)

#Run anova accounting for how many species and how many nodules they sample
#### run this again without mean and accounting for nodule number #### did this above
summary (Mixed_Model_Rhiz_Status_Strain_rich<- lmer(strain_rich_Mean ~ Plant_status + (1 | species_status_n) + (1 | num_nod_Mean), data = Rhiz_symbionts_Nod_Num))
anova(Mixed_Model_Rhiz_Status_Strain_rich,type = 2)
```
